% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = XeLaTeX
% ! xelatex mal-urdu.tex
\documentclass[a4paper, 10pt]{article}

\usepackage{fontspec}
\usepackage{newtxmath}
%\setmainfont{Gentium Plus}
\setmainfont{Charter Regular.ttf}[BoldFont = Charter Bold.ttf , ItalicFont = Charter Italic.ttf , BoldItalicFont = Charter Bold Italic.ttf ]

\usepackage{polyglossia}
\setmainlanguage{english}
\setotherlanguage{urdu}
%\newfontfamily\urdufont[Script=Arabic,Language=Urdu,Scale=1]{Jameel Noori Nastaleeq Kasheeda}
%\newfontfamily\urdufont[Script=Arabic,Language=Urdu,Scale=1]{Jameel Noori Nastaleeq}
\newfontfamily\urdufont[Script=Arabic,Language=Urdu,Scale=1]{alvi-lahori-nastaleeq.ttf}


\usepackage[]{geometry} 
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage[xcdraw,svgnames]{xcolor}
\usepackage{epstopdf}
\usepackage[pdftex]{hyperref}


%\usepackage{times}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\geometry{
 a4paper,
 total={160mm,255mm}}

\title{{\huge Muhammad Yaseen Khan}
 $\cdot$ {\huge\texturdu{محمد یاسین خان}}
%\\\small Academic Curriculum Vit\ae}
\\\small Curriculum Vit\ae}
\author{}
\date{}      

\begin{document}
\maketitle
\vspace{-3em}
\begin{minipage}{0.45\textwidth}
%Centre for Language Computing\\
%Department of Computer Science\\
%Mohammad Ali Jinnah University, Karachi\\
Research \& Development Department\\
Love for Data\\
Pakistan\\
\hfill
\end{minipage}
\hfill
\begin{minipage}{0.45\textwidth}
Tel: \href{tel:+923323240104}{+92-332-3240104}\\
Email: \href{mailto:yaseenkhan.yzai@gmail.com}{yaseenkhan.yzai@gmail.com}\\
Skype: muhammad\_yaseen\_khan\\
URL: \href{https://scholar.google.com/citations?user=a_d2KTEAAAAJ&hl=en}{\textcolor{blue}{Google Scholar}} $\cdot$ \href{https://www.researchgate.net/profile/Muhammad_Yaseen_Khan}{\textcolor{blue}{ResearchGate}} $\cdot$ \href{https://www.github.com/MuhammadYaseenKhan}{\textcolor{blue}{GitHub}}
\end{minipage}

% Educational Background 

\section*{\normalfont\textsc{Educational Background}}
\hfill\begin{minipage}{0.085\textwidth}
Ph.D.\\
MS.SE\\
BS.SE
\end{minipage}%
\begin{minipage}{0.95\textwidth}
Mohammad Ali Jinnah University, 2018--cont'd. 
Advisors: Dr. Tafseer Ahmed and Dr. Shaukat Wasi\\
Karachi Institute of Economics \& Technology, 2014--2015. Advisor: Dr. Khuram N. Junejo\\
University of Karachi, 2007--2010. Advisors: Dr. Humera Tariq and Dr. Tahseen A. Jilani
\end{minipage}


% Experience
\section*{\normalfont\textsc{Position Held}}
\hfill\begin{minipage}{0.23\textwidth}
Feb. 2021-Present\textcolor{lightgray}{\dotfill}\\
Jan. 2017-Feb. 2021\textcolor{lightgray}{\dotfill}\\\\
Jan 2019-Dec. 2019\textcolor{lightgray}{\dotfill}\\
Jan. 2016-Mar. 2017\textcolor{lightgray}{\dotfill}\\
June 2013-Dec. 2016\textcolor{lightgray}{\dotfill}\\\\
Feb. 2012-June. 2013\textcolor{lightgray}{\dotfill}\\\\
Jan. 2011-Feb. 2012\textcolor{lightgray}{\dotfill}\\
July 2010-Dec. 2010\textcolor{lightgray}{\dotfill}\\
Jan. 2010-June 2010\textcolor{lightgray}{\dotfill}\\
\end{minipage}
\begin{minipage}{0.74\textwidth}
Principal R\&D Engineer (for NLP) at Love for Data, Karachi, Pakistan.\\
Senior Lecturer, Department of Computer Science, Faculty of Computing, Mohammad~Ali~Jinnah~University, Karachi.\\
AI/Software Developer, AksIQ.\\
Data Scientist, Cubix Co.\\
Lecturer, College of Computing and Information Sciences, Karachi Institute of Economics and Technology.\\
Software Engineer II, Mazik Global Technologies / Microsoft Inc. / Tyler Technologies Inc.\\
Web and iOS Application Developer, Counterpoint/Qurtaba LLC.\\
Web Developer, Revolutionary Technologies.\\
Web Developer, Sprintech Solutions.\\
\end{minipage}



% Teaching
\section*{\normalfont\textsc{Teaching}}
\hfill\begin{minipage}{0.22\textwidth}
Fall 2020\textcolor{lightgray}{\dotfill}\\
Summer 2020\textcolor{lightgray}{\dotfill}\\
Spring 2020\textcolor{lightgray}{\dotfill}\\
Fall 2019\textcolor{lightgray}{\dotfill}\\
Summer 2019\textcolor{lightgray}{\dotfill}\\
Spring 2019\textcolor{lightgray}{\dotfill}\\\\
Fall 2018\textcolor{lightgray}{\dotfill}\\
Spring 2018\textcolor{lightgray}{\dotfill}\\
Fall 2017\textcolor{lightgray}{\dotfill}\\
Spring 2017\textcolor{lightgray}{\dotfill}\\\\\\
2013--2016\textcolor{lightgray}{\dotfill}\\\\\\
\end{minipage}
\begin{minipage}{0.75\textwidth}
CS6420 Applied Programming; CS1210 Introdcution to Computing\\
CS6420 Applied Programming;\\
CS6420 Applied Programming; CS3310 Artificial Intelligence\\
CS6420 Applied Programming; CS1420 Object-Oriented Programming\\
CS1410 Computer Programming; CS3110 Software Engineering\\
CS6420 Applied Programming; CS6610 Information Retrieval Techniques (co-taught with Dr. S. Wasi); CS2510 Data Structures and Algorithms;\\
CS2510 Data Structures and Algorithms\\
CS1410 Computer Programming\\
CS1410 Computer Programming\\
CS1410 Computer Programming; CS1420 Object-Oriented Programming; CS5339 Introduction to Data Science; CS5510 Advanced Research Method (co-taught with Dr. S. Wasi)\\
Courses taught to undergrad students at KIET in different semesters: Programming Fundamentals; Object-Oriented Programming; Data Structures and Algorithms; Data Mining; Software Engineering.\\% Database and Management Systems; Data Warehousing; Web Engineering; Network Programming; Software Engineering; Design and Analysis of Algorithms; Automata Theory; and Human-Computer Interaction
\end{minipage}

\section*{\normalfont\textsc{Conference and Workshop Committees}}
\begin{enumerate}
\itemsep-4pt
\item Technical committee, 1st Mohammad Ali Jinnah University International Conference on Computing (MAJICC '21), MAJU, Karachi (2021)
\item Organising committee, 1st International Conference on Data Sciences, MAJU, Karachi (2019)
\item Trainer, 1-Day Workshop on Data Science with Python, UBIT, Karachi University (2018)
\item  Trainer, Hands-on Programming with Python, MAJU, Karachi (2018)
\item  Trainer, Programming with Python, Combat:18, KIET, Karachi (2018)
\item  Coach, ICPC 2015 @ NUCES-FAST, Lahore (2015)
\item  Faculty head, CodeJam, PAF-KIET, Karachi (2015)
\item  Faculty head, Combat: The Computing Battle 2017, KIET, Karachi (2014)
\item  Coach, Startup-Weekend, IBA, Karachi (2012)
\end{enumerate}

\section*{\normalfont\textsc{University Committees}}
\begin{enumerate}
\itemsep-4pt 
\item Examination paper moderation committee, MAJU, Karachi (2018--present; \emph{chair}, Spring 2020)
\item Committee on examination policy for COVID-19 pandemic, MAJU, Karachi (\emph{chair}, Spring 2020)
\item QEC Self-Assessment Report for undergrad and grad CS and SE programmes, MAJU, Karachi (member, 2019)
\item External course review committee, KIET, Karachi (2019)
%\item Internal Facilitator for NCEAC, MAJU, Karachi (2019)
\item Graduate thesis evaluation committee, MAJU, Karachi (member, 2018--present)
\item Academic advisor, MAJU, Karachi (2017--persent)
\item Final year project evaluation/exhibition committee, MAJU, Karachi (member, 2017--present)
\item Founding faculty sponsor of ACM-MAJU student chapter, MAJU, Karachi (2017--present)
\item Admission interviews committee, MAJU, Karachi (member, 2017--present)
\item Credit transfer committee, MAJU, Karachi (member, 2018--present)
\item Faculty sponsor of ACM-KIET student chapter, KIET, Karachi (2013--2015)
\item Final year project committee, KIET, (member, 2013--2016)
\end{enumerate}

\section*{\normalfont\textsc{Boards}}
\begin{enumerate}
\itemsep-4pt 
\item Board of Studies, MAJU, Karachi (member, 2017--2019)
\end{enumerate}

\section*{\normalfont\textsc{Publications}}
\vspace{-1em}Items are sorted chronologically in reverse order. Conference papers that later coverted into book chapters or journal articles are counted once.
\subsection*{\normalfont\textsc{ Refereed Journal Articles}}
\begin{enumerate}
\itemsep-4pt 

	\item ``Automated Prediction of Good Dictionary EXamples (GDEX): A Comprehensive Experiment with Distant Supervision, Machine Learning and Word Embedding-based Deep Learning Techniques''. \textcolor{NavyBlue}{M.~Y.~Khan}, A. Qayoom, M. S. Nizami, M. S. Siddiqui, S. Wasi, and S. M. K. R. Raazi; \emph{Complexity}, volume 11, number 11, pages  749--755, 2020. %DOI: \href{https://doi.org/10.1155/2021/}{\textcolor{blue}{doi.org/10.1155/2021/8735625}}. 
(WoS {\bfseries SCIE} indexed /JCR-IF: {\bfseries 2.83})
	
	\item ``Hindustani or Hindi vs. Urdu: A Computational Approach for the Exploration of Similarities Under Phonetic Aspects''. M. S. Nizami, T. Ahmed, and \textcolor{NavyBlue}{M.~Y.~Khan}; \emph{International Journal of Advanced Computer Science and Applications}, volume 11, number 11, pages  749--755, 2020. DOI: \href{https://dx.doi.org/10.14569/IJACSA.2020.0111191}{\textcolor{blue}{10.14569/IJACSA.2020.0111191}}, (WoS {\bfseries ESCI} indexed).
	
	\item ``Edit Distance-based Search Approach for Retrieving  Element-wise Prosody in Hindi/Urdu Poetry''. \textcolor{NavyBlue}{M.~Y.~Khan}, M. A. Rao, S. Wasi, T. A. Minai; \emph{Indian Journal of Science and Technology}, volume 13, number 39, pages  4189--420.
, 2020. (MJL indexed). DOI: \href{https://doi.org/10.17485/IJST/v13i39.1489}{\textcolor{blue}{10.17485/IJST/v13i39.1489}}

	\item ``Exerting 2D-Space of Sentiment Lexicons with Machine Learning Techniques: A Hybrid Approach for Sentiment Analysis''. \textcolor{NavyBlue}{M.~Y.~Khan} and K. N. Junejo; \emph{International Journal of Advanced Computer Science and Applications}, volume 11, number 6, pages 599--608
, 2020. (WoS {\bfseries ESCI} indexed). DOI: \href{https://doi.org/10.14569/IJACSA.2020.0110672}{\textcolor{blue}{10.14569/IJACSA.2020.0110672}}.
       
    \item ``Sentiment Analysis of Product Reviews in the Absence of Labelled Data using Supervised Learning Approaches''. W. Muhammad, M. Mushtaq, K. N. Junejo, and \textcolor{NavyBlue}{M.~Y.~Khan}; \emph{Malaysian Journal of Computer Science}, volume 32, number 2, pages 118--132, 2020. (WoS {\bfseries SCI} indexed). DOI: \href{https://doi.org/10.22452/mjcs.vol33no2.3}{\textcolor{blue}{10.22452/MJCS.vol33no2.3}}. JCR-IF: {\bfseries 0.7}
    
    \item ``Depression Detection using Na\"{\i}ve Bayes: Text based approach''. S. M. Emad, K. Ahsan, \textcolor{NavyBlue}{M.~Y.~Khan}, S. Ahmed, R. Ullah, K. Rizwan, and F. Shafiq; \emph{Interciencia}, volume 44, number 11, pages 174--182, 2020. (WoS JCR-IF: {\bfseries SCIE} indexed). JCR-IF: {\bfseries 0.26}.
	
	\item ``On Extraction of Event Information from Social Text Stream: An Unpretentious NLP Solution''. K. Iqbal, \textcolor{NavyBlue}{M.~Y.~Khan}, S. Wasi, S. Mahboob, and T. Ahmed; \emph{International Journal of Computer Science and Network Security}, volume 19, number 9, pages 121--131, 2019 (WoS {\bfseries ESCI} indexed).
 
	\item ``A Novel Approach For Ontology-Driven Information Retrieving Chatbot For Fashion Brands''. A. Nazir, \textcolor{NavyBlue}{M.~Y.~Khan}, T. Ahmed, S. I. Jami, and S. Wasi; \emph{International Journal of Advanced Computer Science and Applications}, volume 10, number 9, pages 546--552, 2019. (WoS {\bfseries ESCI} indexed). DOI: \href{https://doi.org/10.14569/IJACSA.2019.0100972}{\textcolor{blue}{10.14569/IJACSA.2019.0100972}}.
      
	\item ``Developing Disease Classification System based on Keyword Extraction and Supervised Learning''. M. Suffian, \textcolor{NavyBlue}{M.~Y.~Khan}, and S. Wasi; \emph{International Journal of Advanced Computer Science and Applications}, volume 9, number 9, pages 599--605, 2018. (WoS {\bfseries ESCI} indexed). DOI: \href{https://doi.org/10.14569/IJACSA.2018.090976}{\textcolor{blue}{10.14569/IJACSA.2018.090976}}.
\end{enumerate}


\subsection*{\normalfont\textsc{Refereed Book Chapters}}
\begin{enumerate}
\setcounter{enumi}{9}
\itemsep-4pt 
 \item ``Pseudo Transfer Learning by Exploiting Monolingual Corpus: An Experiment on Roman Urdu Transliteration''. \textcolor{NavyBlue}{M.~Y.~Khan} and T. Ahmed; in: Bajwa I., Sibalija T., Jawawi D. (eds) Intelligent Technologies and Applications. INTAP 2019. \emph{Communications in Computer and Information Science}, vol 1198. Springer, Singapore. DOI \href{https://doi.org/10.1007/978-981-15-5232-8_36}{\textcolor{blue}{10.1007/978-981-15-5232-8\_36}}.
  
   \item ``Towards a Generic Approach for PoS Tag-wise Lexical Similarity of Languages''. M. S. Nizami, \textcolor{NavyBlue}{M.~Y.~Khan} and T. Ahmed; in: Bajwa I., Sibalija T., Jawawi D. (eds) Intelligent Technologies and Applications. INTAP 2019. \emph{Communications in Computer and Information Science}, vol 1198. Springer, Singapore. DOI \href{https://doi.org/10.1007/978-981-15-5232-8_42}{\textcolor{blue}{10.1007/978-981-15-5232-8\_42}}.
   
 \end{enumerate}

\subsection*{\normalfont\textsc{Refereed Conference Publications}}
\begin{enumerate}
\setcounter{enumi}{11}
\itemsep-4pt 

%\item ``Sindhi-English Neural Machine Translation: Dataset and Prefatory Results''. \textcolor{NavyBlue}{M.~Y.~Khan} and Suffian Nizami; \emph{\small submitted.}

%\item ``Deep Learning-based Transliteration of Roman Punjabi into Gurmukhi and Shahmukhi Script''. Suffian Nizami and \textcolor{NavyBlue}{M.~Y.~Khan}; \emph{\small submitted.}


%\item ````To be, or not to be, that is the question'' on Using Word Embeddings and Okapi BM25 in the Development of Urdu Question Answering System''. Muhammad Mazhar Karimi, \textcolor{NavyBlue}{M.~Y.~Khan}, and T. Ahmed; \emph{\small submitted.}

%\item ``Urdu Question Answering System: A Baseline Model''. Muhammad Mazhar Karimi, \textcolor{NavyBlue}{M.~Y.~Khan}, and T. Ahmed; \emph{\small submitted.}

\item ``Classic Fairy Tales / Children Stories of the World: Corpus Organization and Text Analytics''. \textcolor{NavyBlue}{M.~Y.~Khan} and M. U. T. Butt;  in \emph{Proceedings of the 7th International Conference of Linguistic Association of Pakistan (ICLAP '21)}, Sargodha, Pakistan. Nov. 2021. %DOI: \href{https://ieeexplore.ieee.org/document/9526252}{\textcolor{blue}{10.1109/MAJICC53071.2021.9526252}}.


\item ``Using Patient Descriptions of Top-20 Diseases in Text Classification for Evidence-based Medicine''. Samiullah Shaikh,  \textcolor{NavyBlue}{M.~Y.~Khan}, and M. S. Nizami;  in \emph{Proceedings of the 1st Mohammad Ali Jinnah university International Conference on Computing (MAJICC '21)}, Karachi, Pakistan. July. 2021. DOI: \href{https://ieeexplore.ieee.org/document/9526252}{\textcolor{blue}{10.1109/MAJICC53071.2021.9526252}}.

\item ``Processing Fire Detection, Face Recognition, and Head Counting for an IoT-based Application in Emergency Exit''. K. Badr, K. Iqbal, S. Mahboob, and  \textcolor{NavyBlue}{M.~Y.~Khan};  in \emph{Proceedings of the 1st Mohammad Ali Jinnah university International Conference on Computing (MAJICC '21)}, Karachi, Pakistan. July. 2021.  \href{https://ieeexplore.ieee.org/document/9526261}{\textcolor{blue}{10.1109/MAJICC53071.2021.9526261}}.

\item ``Sign Language Translation in Urdu/Hindi Through Microsoft Kinect''. Sohail, \textcolor{NavyBlue}{M.~Y.~Khan}, N. A. Siddiqui, and Kiran; in \emph{Proceedings of the 3rd Pak-Turk Conference On Emerging Technologies}, Ghulam Ishaq Khan Institute of Engineering Sciences and Technology, Pakistan. June. 2020. DOI: \href{https://dpi.org/10.1088/1757-899x/899/1/012016}{\textcolor{blue}{10.1088/1757-899x/899/1/012016}}.

\item ``Urdu~Sentiment~Corpus (v1.0): Linguistic Exploration and Visualization of Labeled Dataset for Urdu~Sentiment~Analysis''. \textcolor{NavyBlue}{M.~Y.~Khan} and M. S. Nizami; in \emph{Proceedings of the 2nd IEEE International Conference On Information Science \& Communication Technology}, Karachi, Pakistan. Feb. 2020. DOI: \href{https://doi.org/10.1109/ICISCT49550.2020.9080043}{\textcolor{blue}{10.1109/ICISCT49550.2020.9080043}}.

% \item ``Pseudo Transfer Learning by Exploiting Monolingual Corpus: An Experiment on Roman Urdu Transliteration''. \textcolor{NavyBlue}{M.~Y.~Khan} and T. Ahmed; in \emph{Proceedings of the 2nd International Conference on Intelligent Technologies and Applications}, Islamia University Bhawalpur, Pakistan. Springer. Nov. 2019.
 
%  \item ``Towards a Generic Approach for PoS Tag-wise Lexical Similarity of Languages''. M. S. Nizami, \textcolor{NavyBlue}{M.~Y.~Khan} and T. Ahmed; in \emph{Proceedings of the 2nd International Conference on Intelligent Technologies and Applications}, Islamia University Bhawalpur, Pakistan. Springer. Nov. 2019.
  
  \item ``Practices for Achieving Accuracy in Software Costing and Estimation''. M. A. Latif, \textcolor{NavyBlue}{M.~Y.~Khan}, and K. Bashir; in \emph{Proceedings of the 2nd International Conference on Computing \& Information Sciences}, Karachi Institute of Economics and Technology, Karachi, Pakistan. Nov. 2018.
  
  \item ``Drive pattern analyzer using smartphones''. S. Mahboob, K. Iqbal, H. Farman, \textcolor{NavyBlue}{M.~Y.~Khan}, and S. Wasi; in \emph{ Proceedings of the 13th IEEE International Conference on Emerging Technologies}, Capital University of Science and Technology, Islamabad, Pakistan. IEEE, pages 1-5, 2017. DOI: \href{https://doi.org/10.1109/ICET.2017.8281659}{\textcolor{blue}{10.1109/ICET.2017.8281659}}.
  
  \item ``Harnessing English Sentiment Lexicons for Polarity Detection in Urdu Tweets: A Baseline Approach''. \textcolor{NavyBlue}{M.~Y.~Khan}, S. M. Emaduddin, and K. N. Junejo;  in \emph{Proceedings of the 11th IEEE International Conference on Semantic Computing}, San Diago, USA. IEEE, pages. 242-24, 2017. DOI: \href{https://doi.org/10.1109/ICSC.2017.68}{\textcolor{blue}{10.1109/ICSC.2017.68}}.
\end{enumerate}

\subsection*{\normalfont\textsc{ Unpublished Work}}
\begin{enumerate}
\setcounter{enumi}{19}
\itemsep-4pt 

	\item ``Discovering Lexical Similarity Through Articulatory Feature-based Phonetic Edit Distance''. T. Ahmed, M. S. Nizami, \textcolor{NavyBlue}{M.~Y.~Khan}; \textcolor{blue}{\url{https://arxiv.org/abs/2008.06865}}.
	
	\item ``Developing Senitment Lexicon and Labelled Corpus for Urdu Sentiment Analysis''. \textcolor{NavyBlue}{Muhammad~Yaseen Khan}, R. Zaheer; \emph{\small experimentation completed; in draft.}
	
	\item ``Developing Emotion Lexicon and Labelled Corpus for Urdu Emotion Detection''. \textcolor{NavyBlue}{Muhammad Yaseen Khan}, T. Khalid; \emph{\small experimentation completed; in draft.}	

	\item ``Urdu Named-Entity Recognition System''. T. Ahmed, \textcolor{NavyBlue}{M.~Y.~Khan}, and S. Nizami; \emph{\small experimentation completed; in draft.}
	
	\item ``LSTM-based Urdu Word Segmentation''. \textcolor{NavyBlue}{M.~Y.~Khan} and T. Ahmed; \emph{\small experimentation completed; in draft.}
	
	\item ``Depressive Sentiment Analysis in Microblogs: A Machine Learning Approach''. S. M. Emaduddin, K. Ahsan, \textcolor{NavyBlue}{M.~Y.~Khan}, and S. Ahmed; \emph{\small under review.}
	
	\item ``Efficient Recipe Recommendation System Using Signature-Trees''. A. Sohani, \textcolor{NavyBlue}{M.~Y.~Khan}, and R. Ullah; 
	%\emph{University of Sindh Journal of Information and Communication Technology} 
	\emph{\small accepted with revision.}
	
	


\end{enumerate}


\subsection*{\normalfont\textsc{Conference and Workshop Attendee}}
\begin{enumerate}
\itemsep-4pt
\item 7th Intl. Conf. of Linguistics of Pakistan (ICLAP), Univesity of Sargodha, Pakistan (2021)
\item 1st Mohammad Ali Jinnah Univesity Conf. on Computing (MAJICC), Karachi, Pakistan (2021)
\item 7th Intl. Conf. on Language and Technology (CLT), CLE-UET, Lahore (2020)
\item 2nd Intl. Conf. on Information Science \& Communication Technology (ICISCT), UoK, Karachi, Pakistan (2020)
\item 2nd Intl. Conf. on Intelligent Technologies and Applications (INTAP), IUB, Bhahawalpur (2019)
\item 1st Intl. Conf. on Data Science, MAJU, Karachi, Pakistan (2019)
\item 2nd Intl. Conf. on Computing and Information Sciences, KIET, Karachi, Pakistan (2018)
\item HEC-NCEAC 3-Day Workshop on Data Science, Islamabad (2017) 
\end{enumerate}

%\section*{\normalfont\textsc{Current Students}}
%\begin{enumerate}
%\itemsep-4pt 
%\end{enumerate}

\section*{\normalfont\textsc{Graduated Students}}
\begin{enumerate}
\itemsep-4pt 
 \item M. S. Nizami (MS Thesis - CS); ``Formulating Patient Descriptions to Support Evidence Based Medicine''. Spring 2018. Co-supervised by Dr S. Wasi.

 \item Alvina Naveed (MS Thesis - SE); ``Exploiting Bug Narrations for Predictive Analysis on Bug Severity''. Fall 2020.

 \item Abdul Basit (MS Thesis - CS); ``Human motion tracking for gait analysis through smart phones and machine learning approaches''.  Fall 2020.

  \item Abdul Qayoom Bhatti (MS Thesis - CS); ``Supervised Learning-based Good Dictionary Examples Recommendation System''.  Fall 2020. 
  
  \item Mirza Muhammad Muneeb Baig (MS Thesis - CS); ``Sarcasm detection in Urdu Text''. Fall 2020.
\end{enumerate}


\section*{\normalfont\textsc{Awards and Honours}}
\begin{enumerate}
\itemsep-4pt 
 \item Awardee of Dean's List 2014 and 2015 during MS.SE, KIET
\end{enumerate}

\section*{\normalfont\textsc{Research Interests}}
%Artificial Neural Networks/Deep Learning $\cdot$ 
Natural Language Processing $\cdot$ Information Extraction $\cdot$ Information Retrieval $\cdot$ Affective Computing in Text $\cdot$ Lexical Analysis $\cdot$ Discourse Analysis $\cdot$ Computational Linguistics $\cdot$  Corpus Linguistics $\cdot$ Sociolinguistics $\cdot$ NLP for scared source Indic languages (specifically languages in Perso-Arabic scripts)

\section*{\normalfont\textsc{Skills}}
\hfill\begin{minipage}{0.17\textwidth}
Computing\textcolor{lightgray}{\dotfill}\\
Languages\textcolor{lightgray}{\dotfill}
\end{minipage}%
\begin{minipage}{0.8\textwidth}
Programming (Python, Java, JavaScript, C\#, MySQL) $\cdot$ Typesetting with \LaTeX\\
English $\cdot$ Urdu $\cdot$ Hindi $\cdot$ Persian/Farsi %$\cdot$ Pushto  Arabic $\cdot$$\cdot$ Sindhi $\cdot$ Punjabi
\end{minipage}

\section*{\normalfont\textsc{References}}
\begin{enumerate}
\itemsep-4pt
 \item Dr. Tafseer Ahmed Khan, Professor and Head Center for Language Computing, MAJU, Karachi.
 \item Dr. Shaukat Wasi, Professor and Dean Faculty of Computing, MAJU, Karachi.
 \item Dr. Asim Imdad Wagan, Professor and Dean Faculty of Engineering, MAJU, Karachi.
 \item Dr. Khurum Nazir Junejo, Head of R\&D at Love for Data.
 \item Dr. Muhammad Khalid Khan, Professor and Director CoCIS, PAF-KIET, Karachi.
\end{enumerate}

\end{document}  